### 2021-05-04 docs/manuscript/PLOS-MSc-Thesis.tex
Explain heatmap in Fig1.D
Improve Fig3 caption
- Explain that each node is a topology
- Say that most abundant topologies are depicted as
in Fig1.

\begin{figure}[!h]
%  \centering
 \includegraphics[width=\textwidth]{figures/metodos/Fig1}
    \caption{\bf Modelling of GRNs.}
    (A) GRN represented as a directed graph with activation (blue arrows) and
    inhibition (red arrows) interactions. Black circles
    tagged with a \textbf{M} represent the morphogen; \textbf{A}, \textbf{B} and
    \textbf{C} represent genes in the network.
    (B) The same GRN represented as an adjacency matrix in which positive values
    represent activation, negative ones represent inhibition and
    zeros represent no interaction.
    (C) Morphogenetic field. In our model the field was composed of a linear
    array of 30 isogenic cells and a morphogen gradient concentration described
    by an exponential decay function. Horizontal arrows between cells represent
    diffusion of gene products between adjacent cells. Optimal gene expression
    pattern is shown top right.
    (D) Spatiotemporal expression profile of a GRN.
 \label{fig:model}
\end{figure}

@@

\begin{figure}[!h]
 \includegraphics[width=\textwidth]{figures/results/Fig3}
 \caption{\bf Neutral network.}
 This graph shows network topologies connected by one mutational step. Most
 abundant network topologies are shown as black nodes. All nodes with the same
 color belong to a cluster of nodes more connected between them than with other
 nodes in the graph.
 \label{fig:neutral-network}
\end{figure}

>>>>

\begin{figure}[!h]
%  \centering
 \includegraphics[width=\textwidth]{figures/metodos/Fig1}
    \caption{\bf Modelling of GRNs.}
    (A) GRN represented as a directed graph with activation (blue arrows) and
    inhibition (red arrows) interactions. Black circles
    tagged with a \textbf{M} represent the morphogen; \textbf{A}, \textbf{B} and
    \textbf{C} represent genes in the network.
    (B) The same GRN represented as an adjacency matrix in which positive values
    represent activation, negative ones represent inhibition and
    zeros represent no interaction.
    (C) Morphogenetic field. In our model the field was composed of a linear
    array of 30 isogenic cells and a morphogen gradient concentration described
    by an exponential decay function. Horizontal arrows between cells represent
    diffusion of gene products between adjacent cells. Optimal gene expression
    pattern is shown top right.
    (D) Heatmap of spatiotemporal expression profile of a GRN where blue
    colors represent lower expression and red colors represent higher
    expression.
 \label{fig:model}
\end{figure}

@@

\begin{figure}[!h]
 \includegraphics[width=\textwidth]{figures/results/Fig3}
 \caption{\bf Neutral network.}
 This graph shows network topologies connected by one mutational step, where
 each node represents a single topology. Black nodes represent the most
 abundant topologies. All nodes with the same
 color belong to a cluster of nodes more connected between them than with other
 nodes in the graph. The most abundant topologies are represented as
 directed graphs in the same way as in Fig~\ref{fig:model}A, except for
 the topologies 1 to 8 and 15 (orange and red clusters), in which only
 topology 1 is depicted.
 \label{fig:neutral-network}
\end{figure}
